--- 
title: "STICS intercrop: a work in progress for the ReMIX H2020 project"
author: "R. Vezy"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This book is made to keep track of the work made during the post-doctorate position on STICS-intercrop for the ReMIX project."
---

```{r, include=FALSE}
if(knitr:::pandoc_to() == "html") {
  knitr::opts_chunk$set(echo = TRUE)
}else{
  knitr::opts_chunk$set(echo = FALSE)
}
```

# Prerequisites

Each chapter of the book match a specific objective. I first introduce the subject with a brief description, try to find some solutions for the specific issues and show the results. 

The code is only visible on the `html` version of the book, so please refer to this format if you need any further information (open the `index.html` file).

This book is written using the R **bookdown** package, which can be installed from CRAN or Github:

```{r eval=FALSE, include=TRUE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```



```{r setup, include=FALSE}
# Add a common class name for every chunks
knitr::opts_chunk$set(
  echo = TRUE)
```

